Standardized crypto-loans on\\ the Cardano blockchain

### 2021-02-04 papers/actus2021/article.tex

Using static analysis for Marlowe~\cite{marlowe-efficient} it is possible fully to check a particular contract instead of using random
sampling. That would allow some refinements: 
\begin{itemize}
\item More balanced sampling: the space of contract terms depends linearly on
the coverage, e.g. if we cover 10\% of all possible contract terms
- we'll cover 10\% of all contracts. Different contracts have different
sets of risk factors, and so different search spaces. For instance, a
contract with 3 risk factors (e.g. 3 observations of an interest rate)
would span over $n^3$ values while a contract with 10 risk
factors would span over $n^{10}$. Meanwhile, the space of
all risk factors in all contracts doesn't linearly depend on the coverage.
% SJT explain last sentence. 
\item Dependency tracking: an SMT-solver is potentially likely to be more aware of execution
paths that lead to the failure of a test, a feature that could significantly reduce
search space. 
\item Completeness: if not timed out, SMT-solving is decidable while sampling
is semi-decidable. 
\end{itemize}

>>>>

Using static analysis for Marlowe~\cite{marlowe-efficient} it is possible fully to check a particular contract instead of using random
sampling. That would allow some refinements: 
\begin{itemize}
\item More balanced sampling: the space of contract terms depends linearly on
the coverage, e.g. if we cover 10\% of all possible contract terms
- we'll cover 10\% of all contracts. Different contracts have different
sets of risk factors, and so different search spaces. For instance, a
contract with 3 risk factors (e.g. 3 observations of an interest rate)
would span over $n^3$ values while a contract with 10 risk
factors would span over $n^{10}$. Meanwhile, the space of
all risk factors in all contracts doesn't linearly depend on the coverage - some contracts might have more risk factor observations and some - less. So covering 10\% of all contracts doesn't necessary mean covering 10\% of all possible observations.
% SJT explain last sentence. 
% dk14 added explanation. Maybe it could be phrased better. The idea is that if I have contracts A and B as population and only A is covered then coverage is 50%. Meanwhile contract A has 9 observatioins and B has 1 so risk factors have 90% coverage. Idk how to put it nicely.
\item Dependency tracking: an SMT-solver is potentially likely to be more aware of execution
paths that lead to the failure of a test, a feature that could significantly reduce
search space. 
\item Completeness: if not timed out, SMT-solving is decidable while sampling
is semi-decidable. 
\end{itemize}
